\Large Feature and order manipulations in a free recall task affect memory for current and future lists

### 2023-11-21 paper/main.tex
highlight significant rows in tables

%! suppress = LineBreak
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage[sort&compress]{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{amsopn}
\usepackage{rotating}
\usepackage{booktabs}

@@

We next asked whether adding these incidental visual features to later lists
(after the participants had already studied impoverished lists), or removing
the visual features from later lists (after the participants had already
studied visually diverse lists) might affect memory performance. In other
words, we sought to test for potential effects of changing the ``richness'' of
participants' experiences over time. All participants studied and recalled a
total of 16 lists; we defined \textit{early} lists as the first eight lists and
\textit{late} lists as the last eight lists each participant encountered. To
help interpret our results, we compared participants' memories on early versus
late lists in the above feature-rich
(Tab.~\ref{tab:early-vs-late-feature-rich}) and reduced
(Tab.~\ref{tab:early-vs-late-reduced}) conditions. Participants in both
conditions remembered more words on early versus late lists. Participants in
the feature-rich (but not reduced) conditions exhibited more temporal
clustering on early versus late lists. And participants in both conditions
tended to exhibit more semantic clustering on early versus late lists.
Participants in the reduced (but not feature-rich) conditions tended to exhibit
more lexicographic clustering on early versus late lists. Taken together, these
comparisons suggest that even when the presence or absence of incidental visual
features is stable across lists, participants still exhibit some differences in
their performance and memory organization tendencies for early versus late
lists.

@@

Contextual features need not be intentionally or consciously perceived by the
participant to affect memory, nor do they need to be relevant to the task
instructions or the participant's goals. Incidental factors such as font
color~\citep{JonePyc14}, background color~\citep{IsarIsar07}, inter-stimulus
images~\citep{GersEtal13, MannEtal16, ChiuEtal21}, background
sounds~\citep{BeamJone10, SahaSmit14}, secondary tasks~\citep{MasiSaha14,
PolyEtal09, OberLewa08}, and more can all impact how participants remember, and
organize in memory, lists of studied items.

>>>>

%! suppress = LineBreak
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage[sort&compress]{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{amsopn}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage[table]{xcolor}

@@

Beyond affecting participants' memories for individual lists, we wondered how
studying early lists (with versus without incidental visual features) might
affect how participants remembered later lists (again, with versus without
incidental visual features). In other words, we sought to test for potential
effects of changing the ``richness'' of participants' experiences over time.
All participants studied and recalled a total of 16 lists; we defined
\textit{early} lists as the first eight lists and \textit{late} lists as the
last eight lists each participant encountered. To help interpret our results,
we compared participants' memories on early versus late lists in the above
feature-rich (Tab.~\ref{tab:early-vs-late-feature-rich}) and reduced
(Tab.~\ref{tab:early-vs-late-reduced}) conditions. Participants in both
conditions remembered more words on early versus late lists. Participants in
the feature-rich (but not reduced) condition exhibited more temporal
clustering on early versus late lists. And participants in both conditions
tended to exhibit more semantic clustering on early versus late lists.
Participants in the reduced (but not feature-rich) conditions tended to exhibit
more lexicographic clustering on early versus late lists. Taken together, these
comparisons suggest that even when the presence or absence of incidental visual
features is stable across lists, participants still exhibit some differences in
their performance and memory organization tendencies for early versus late
lists.

@@

Contextual features need not be intentionally or consciously perceived by the
participant to affect memory, nor do they need to be relevant to the task
instructions or the participant's goals. Incidental factors such as font
color~\citep{JonePyc14}, background color~\citep{IsarIsar07}, inter-stimulus
images~\citep{GersEtal13, MannEtal16, ChiuEtal21}, background
sounds~\citep{BeamJone98, SahaSmit14}, secondary tasks~\citep{MasiSaha14,
PolyEtal09, OberLewa08}, and more can all impact how participants remember, and
organize in memory, lists of studied items.
